---
title: "Mid_an_milestone"
author: "Gabriela Caballero"
date: "10/11/2020"
output: html_document
---

```{r setup, include=FALSE}
milestones<-read.csv("~/Documents/NYU Fall 2020/BA/05_tb_mid_ana_milestone.csv", header=T, na.strings=c("","NA"))

```

Created Applications by Month
```{r, include=FALSE}
#library(ggplot2)
#milestones$milestone_created_date<-sub("33:47.0","NA",milestones$milestone_created_date)
#milestones$milestone_created_date<- as.Date(milestones$milestone_created_date,"%m/%d/%y")
#milestones$createdMonth<-months(milestones$milestone_created_date)
#applCreatedByMonth<-aggregate(milestones$element_id,by=list(milestones$createdMonth),FUN="length")
#applCreatedByMonth$Group.1 <- factor(applCreatedByMonth$Group.1,levels = c("January", "February", "March", "April","May", "June","July","August","September","October","November","December"))
#ggplot(applCreatedByMonth,aes(x=Group.1,y=x)) +
#geom_bar(stat="identity",width=0.5) +
#ggtitle("Applications Created by Month") + ylim(0,15500)
```
Applications started by month
```{r}
library(ggplot2)

milestones$milestone_application_start_date<-as.Date(milestones$milestone_application_start_date,"%m/%d/%y")
#Extracting months from the start application date
milestones$createdMonth<-months( milestones$milestone_application_start_date)
#Counting applications started by month

applCreatedByMonth<-aggregate(na.omit(milestones$element_id),by=list(milestones$createdMonth),FUN="length")
applCreatedByMonth
#Ordering 
applCreatedByMonth$Group.1 <- factor(applCreatedByMonth$Group.1,levels = c("January", "February", "March", "April","May", "June","July","August","September","October","November","December"))
#Ploting
ggplot(applCreatedByMonth,aes(x=Group.1,y=x)) +
geom_bar(stat="identity",width=0.5) +
ggtitle("Applications Started by Month") + ylim(0,max(applCreatedByMonth$x))
```





#AVG time to complete an application in months
```{r cars}
#Converting into date format
milestones$milestone_application_complete_date<-as.Date(milestones$milestone_application_complete_date,"%m/%d/%y")
milestones$milestone_application_start_date<-as.Date(milestones$milestone_application_start_date,"%m/%d/%y")
milestones$daysToCompleteApl<-as.numeric( milestones$milestone_application_complete_date - milestones$milestone_application_start_date)
#Average days to complete an application
summary(milestones$daysToCompleteApl)
boxplot(milestones$daysToCompleteApl)

```

##Percentage of applications started that end up being submited 

```{r}

appStarted=subset(milestones,!is.na(milestones$milestone_application_start_date))
appSubmited=subset(milestones,!is.na(milestones$milestone_application_submit_date))
appDiscarded=length(appStarted$element_id)-length(appSubmited$element_id)
#PercApSubmited=(length(appSubmited$element_id)*100)/length(appStarted$element_id)
#PercApDiscarded=appStarted- PercApSubmited
slices <- c(length(appSubmited$element_id), appDiscarded)
lbls<-c("Applications submited","Applications discarded")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="") # ad % to labels
pieChart=pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Applications submitted")

```

#Applications submitted that are admited
```{r}
appsAdmited=subset(milestones,!is.na(milestones$milestone_admit_date))
appsDenied=subset(milestones,!is.na(milestones$milestone_denied_date))
PercApAdmited=length(appsAdmited$element_id)
PercApDenied=length(appsDenied$element_id)
PercpApsUnk=length(appStarted$element_id)-(PercApAdmited+PercApDenied)
slices2 <- c(PercApAdmited, PercApDenied,PercpApsUnk)
lbls2<-c("Applications Admited","Applications Denied","Applications without information")
pct2 <- round(slices2/sum(slices2)*100)
lbls2 <- paste(lbls2, pct2) # add percents to labels
lbls2 <- paste(lbls2,"%",sep="") # ad % to labels
pieChart2=pie(slices2,labels = lbls2, col=rainbow(length(lbls2)),
   main="Pie Chart of Admited and Denied Applications")
```
#Applications admitted per month
```{r}
library(ggplot2)

milestones$milestone_admit_date<-as.Date(milestones$milestone_admit_date,"%m/%d/%y")
#Extracting months from the admitions application date
milestones$admitedMonth<-months( milestones$milestone_admit_date)
#Counting applications admited by month

applAdmitedByMonth<-aggregate(na.omit(milestones$element_id),by=list(milestones$admitedMonth),FUN="length")
applAdmitedByMonth
#Ordering 
applAdmitedByMonth$Group.1 <- factor(applAdmitedByMonth$Group.1,levels = c("January", "February", "March", "April","May", "June","July","August","September","October","November","December"))
#Ploting
ggplot(applAdmitedByMonth,aes(x=Group.1,y=x)) +
geom_bar(stat="identity",width=0.5) +
ggtitle("Applications Admited by Month") + ylim(0,max(applAdmitedByMonth$x))
```
#Applicants admited that end up enrolling and withdrawing
```{r}
#Converting into date format
appsEnrolled=subset(milestones,!is.na(milestones$milestone_enroll_date))
PercApEnrolled=length(appsEnrolled$element_id)
appsWithdraw=subset(milestones,!is.na(milestones$milestone_withdraw_date))
PercApWithdrawed=length(appsWithdraw$element_id)
PerceApAdmitUnkonw=length(appsAdmited$element_id)-(PercApEnrolled+PercApWithdrawed)
PercApEnrolled
PercApWithdrawed
PerceApAdmitUnkonw
slices3 <- c(PercApEnrolled, PercApWithdrawed, PerceApAdmitUnkonw)
lbls3<-c("Applicants Enrolled","Applications Withdrawed", "Applications without info")
pct3 <- round(slices3/sum(slices3)*100)
lbls3 <- paste(lbls3, pct3) # add percents to labels
lbls3 <- paste(lbls3,"%",sep="") # ad % to labels
pieChart3=pie(slices3,labels = lbls3, col=rainbow(length(lbls3)),
   main="Pie Chart of Enrolled and Wirdrawed Applications")
```

#Enrollings per Month
```{r}
library(ggplot2)

milestones$milestone_enroll_date<-as.Date(milestones$milestone_enroll_date,"%m/%d/%y")
#Extracting months from the enrolled application date
milestones$enrollMonth<-months( milestones$milestone_enroll_date)
#Counting applications enrolled by month

applEnrolledByMonth<-aggregate(na.omit(milestones$element_id),by=list(milestones$enrollMonth),FUN="length")
applEnrolledByMonth
#Ordering 
applEnrolledByMonth$Group.1 <- factor(applEnrolledByMonth$Group.1,levels = c("January", "February", "March", "April","May", "June","July","August","September","October","November","December"))
#Plotting
ggplot(applEnrolledByMonth,aes(x=Group.1,y=x)) +
geom_bar(stat="identity",width=0.5) +
ggtitle("Applications Enrolled by Month") + ylim(0,max(applEnrolledByMonth$x))
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
